---
output:
  pdf_document: default
  html_document: default
---
install.packages("tinytex")

---
title: "QMM1002 Case Study  1 [20%]"
author:
- Rashmi Jaiswal
- A00254769
date: 'Due: February 22, 2022 at 11:59PM'
output:
  pdf_document: default
  word_document: default
  html_document: default
extra_dependencies: xcolor
---

**<span style="color: #8F2050;">This is a template to guide your creation of a RMarkdown file. You must erase all question references and explanations related to using RMarkdown.</span>**

## Introduction

In QMM1001 we collected personalized data to analyze. We will continue this analysis in QMM1002. Using RMarkdown, you can show your code and output from R directly in your report. 

In the introduction section, you must describe the variables you collected. You can include a list of your variables in an RMarkdown table.
I have collected data for data for Date, Number of hours on Zoom, Hours spend studying, Hours spent sleeping, Cups to tea, Watched news and The 3 personalized variables of my choice are Lunch Meal, Spice Level of the Lunch Mean, and Number of Video Calls. I choose these as I wanted to understand the dishes I make and how much spice level I make a particular dish and measure the number of video calls I make every day

Variable | Type
------------- | -------------
Date | Identifier
Zoom  | Quantitative
Study  | Quantitative
Sleep | Quantitative
Tea | Quantitative
News | Categorical
Lunch Meal Homemade  | Categorical
Spice Level of the Lunch.Meal  | Categorical
Number of video Calls  | Quantitative
Term (S22 or F22) | Categorical



The variables that will be analyzed are hours spent studying, hours sleeping, and Number of video Calls made in a day

You must also include calculations of summary statistics. This is how you run code in RMarkdown. Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the summary statistics, only the output is shown.

**Summary Statistics**

```{r echo=FALSE}
rashmi<-read.csv(file="Personalized Data Rashmi Jaiswal.csv", header=TRUE)
rashmi.3vars<-subset(rashmi, select=c("Number.of.video.Calls", "Study", "Sleep"))
summary(rashmi.3vars)
```

Equations can be written easily in RMarkdown - for example if you wanted to show the calculation for the mean it is $\bar y = \frac{\Sigma y}{n}$.

You must also check the four conditions required to use the t-distribution. To do this, you will need to create plots as below. Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Conditions and Assuptions for T-test

### Study
#### Condition1 : Independent Assumption: The data for study is independent of other varia

#### Condition2 : Randomization Assumption: The data is not random. It is complete data for assumption
#### Condition3 : 10% condition: The data is not large and is data is related to only me

#### Condition4 : Nearly Normal Condition: The data for study is not nearly normally distributed. 
```{r echo=FALSE}
#Show output only
hist(rashmi$Study, xlab="Study", main="Study Hours Each Day")
boxplot(rashmi$Study, ylab="Study", main="Study Hours Each Day")
```

### Sleep
#### Condition1 : Independent Assumption: The data for Sleep is independent.

#### Condition2 : Randomization Assumption: The data is not random. It is complete data for assumption
#### Condition3 : 10% condition: The data is not large and is data is related to only me

#### Condition4 : Nearly Normal Condition: The data for Sleep is nearly normally distributed and right skewed  

```{r echo=FALSE}
#Show output only
hist(rashmi$Sleep, xlab="Sleep", main="Sleep Hours Each Day")
boxplot(rashmi$Sleep, ylab="Sleep", main="Sleep Hours Each Day")
```
### Number of video call per day
#### Condition1 : Independent Assumption: The data for Number of video call per day is independent of other variables 
#### Condition2 : Randomization Assumption: The data is not random. It is complete data for assumption
#### Condition3 : 10% condition: The data is not large and is data is related to only me

#### Condition4 : Nearly Normal Condition: The data for Sleep is not nearly normally distributed but left skewed
```{r echo=FALSE}
#Show output only
hist(rashmi$Number.of.video.Calls, xlab="Number of video call per day", main="Sleep Hours Each Day")
boxplot(rashmi$Number.of.video.Calls, ylab="Number of video call per day", main="Sleep Hours Each Day")
```

Your must check all four conditions for each variable. If a condition is not met, you must comment on how the data collection methods could be changed to ensure that the conditions hold.


## Data Analysis
Don't forget you must include more than 5 examples of your daily activities that help to explain the results of your analysis for full marks in this section!

### Part 1: Confidence Intervals
#### Study
Place your analysis here.

```{r include=FALSE}
#Hide all output but extract the confidence interval from this in the interpretation below
study.conf<-t.test(rashmi$Study, conf.level = 0.95)
```

The 95% confidence interval is between `r study.conf$conf.int` hours.

#### Sleep
Place your analysis here.

```{r include=FALSE}
#Hide all output but extract the confidence interval from this in the interpretation below
sleep.conf<-t.test(rashmi$Sleep, conf.level = 0.95)
```

The 95% confidence interval is between `r sleep.conf$conf.int` hours.

#### Video Calls
Place your analysis here.

```{r include=FALSE}
#Hide all output but extract the confidence interval from this in the interpretation below
calls.conf<-t.test(rashmi$Number.of.video.Calls, conf.level = 0.95)
```

The 95% confidence interval is between `r calls.conf$conf.int` hours.

### Part 2: One-Sample Hypothesis Tests

Place your analysis here.

You can also easily write hypotheses in R. For example:

$H_0: \mu = 0$

$H_A: \mu \neq 0$

```{r include=FALSE}
#Hide all output but extract the confidence interval from this in the interpreration below
j.test<-t.test(jenna$Study, alternative="greater", mu = 3.13)
```

The p-value from performing the test at $\alpha = 0.05$ is `r j.test$p.value`.

### Part 3: Two-Sample Hypothesis Tests

Place your analysis here. The first step is to make subsets. We started the process during our live class.

```{r include=FALSE}
#create subsets by term
jFall<-subset(jenna, Term=="F21", select="Study")
jWinter<-subset(jenna, Term=="W22", select="Study")

#part 3.2 - create a random sample of 10 days from each subset
jFall3.2<-sample(jFall$Study, 10)
jWinter3.2<-sample(jWinter$Study, 1)

#part 3.3 - select the first 10 days from each subset
jFall3.3<-jFall[1:10,1]
jWinter3.3<-jWinter[1:10,1]
```

## Conclusion
Summarize all the questions investigated and your main findings about the three quantitative variables investigated. 
